Exploring dimensions of biodiversity in Japanese ferns

### 2020-07-04 ms/manuscript.Rmd
Change metrics to all richness-based measures
no MPD or MNTD

map_theme <- theme(
    panel.grid.major = element_line(color = "white", size = 0.2),
    axis.ticks = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.7)
  )

@@

```{r diversity, fig.width = 7, fig.height = 9}
# Richness
a <- ggplot(ses_div_ferns_spatial, aes(fill = richness)) +
  geom_sf(color = "transparent") +
  scale_fill_viridis_c() +
  labs(fill = "Richness \n (n spp.)") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme +
  theme(
    axis.text.x = element_blank()
  )

# Sampling rendundancy
b <- ggplot(ses_div_ferns_spatial, aes(fill = redundancy)) +
  geom_sf(color = "transparent") +
  scale_fill_viridis_c() +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  labs(fill = "Redundancy") +
  map_theme +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank()
  )

# MPD
c <- ggplot(ses_div_ferns_spatial, aes(fill = mpd_obs)) +
  geom_sf(color = "transparent") +
  labs(fill = "MPD") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  scale_fill_viridis_c() +
  map_theme +
  theme(
    axis.text.x = element_blank()
  )

# SES MPD
d <- ggplot(ses_div_ferns_spatial, aes(fill = mpd_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES MPD") +
  scale_fill_scico(
    palette = "romaO",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, pd_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, pd_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank()
  )

# Raw morph diversity
e <- ggplot(ses_div_ferns_spatial, aes(fill = mpd_morph_obs)) +
  geom_sf(color = "transparent") +
  labs(fill = "MMD") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  scale_fill_viridis_c() +
  map_theme +
  theme(
    axis.text.x = element_blank()
  )

# SES of morph diversity
f <- ggplot(ses_div_ferns_spatial, aes(fill = mpd_morph_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES MMD") +
  scale_fill_scico(
    palette = "romaO",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, mpd_morph_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, mpd_morph_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank()
  )

g <- ggplot(ses_div_ferns_spatial, aes(fill = pd_obs)) +
  geom_sf(color = "transparent") +
  labs(fill = "MMD") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  scale_fill_viridis_c() +
  map_theme

h <- ggplot(ses_div_ferns_spatial, aes(fill = pd_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES PD") +
  scale_fill_scico(
    palette = "romaO",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, pd_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, pd_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme +
  theme(
    axis.text.y = element_blank()
  )

@@

**`r figure("diversity")`**. `r figure_cap("diversity")` **A**, richness. **B**, sampling redundancy. **C**, mean phylogenetic distance (MPD). **D**, Standard effect size (SES) of MPD. **E**, mean morphological distance (MMD) **F**, SES of MMD. **G**, phylogenetic diversity (PD) **H**, SES of PD.

@@

```{r endemism, fig.width = 7, fig.height = 8}
# PE
a <- ggplot(ses_div_ferns_spatial, aes(fill = pe_obs)) +
  geom_sf(color = "transparent") +
  scale_fill_viridis_c() + 
  labs(fill = "PE") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme +
  theme(
    axis.text.x = element_blank()
  )

# SES PE
b <- ggplot(ses_div_ferns_spatial, aes(fill = pe_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES PE") +
  scale_fill_scico(
    palette = "romaO",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, pe_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, pe_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme +
  theme(
    axis.text.y = element_blank()
  )

# RPE
c <- ggplot(ses_div_ferns_spatial, aes(fill = rpe_obs)) +
  geom_sf(color = "transparent") +
  scale_fill_viridis_c() + 
  labs(fill = "RPE") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme +
  theme(
    axis.text.x = element_blank()
  )

# SES RPE
d <- ggplot(ses_div_ferns_spatial, aes(fill = rpe_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES RPE") +
  scale_fill_scico(
    palette = "romaO",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, rpe_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, rpe_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme +
  theme(
    axis.text.y = element_blank()
  )

# CANAPE
e <- ggplot(ses_div_ferns_spatial, aes(fill = endem_type)) +
  geom_sf(color = "transparent") +
  labs(fill = "Endemism\ntype") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme

@@

```{r bioregions, fig.width = 7, fig.height = 3}
# Taxonomic bioregions
a <- ggplot(ses_div_ferns_spatial, aes(fill = taxonomic_cluster)) +
  geom_sf(color = "transparent") +
  scale_fill_carto_d(name = "Cluster", type = "qualitative", palette = "Bold") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme

# Phylogenetic bioregions
b <- ggplot(ses_div_ferns_spatial, aes(fill = phylo_cluster)) +
  geom_sf(color = "transparent") +
  labs(fill = "Cluster") +
  scale_fill_carto_d(name = "Cluster", type = "qualitative", palette = "Bold") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme

@@

```{r diversity-by-cluster}
ses_div_ferns_spatial %>%
  filter(taxonomic_cluster %in% c(1,2,3,4)) %>%
  as_tibble %>%
  select(mpd_obs_z, mpd_morph_obs_z, pe_obs_z, taxonomic_cluster) %>%
  pivot_longer(names_to = "var", values_to = "value", -taxonomic_cluster) %>%
  ggplot(aes(x = taxonomic_cluster, y = value)) +
  geom_jitter() +
  geom_boxplot(color = "grey80", fill = "transparent", outlier.shape = NA, alpha = 0.5) +
  facet_wrap(vars(var)) +
  theme(
    panel.grid.minor.x = element_blank(),
    panel.grid.major.x = element_blank(),
  )
```

Standard effect size (SES) of mean phylogenetic distance (MPD), mean morphological distance (MMD), and phylogenetic endemism (PE) by taxonomic bioregion (top four regions with the most sites only shown).

>>>>

map_theme <- theme(
    panel.grid.major = element_line(color = "grey95", size = 0.1),
    panel.background = element_rect(fill = "grey60"),
    axis.ticks = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.7)
  )

map_theme_light <- theme(
    panel.grid.major = element_line(color = "white", size = 0.1),
    panel.background = element_rect(fill = "grey90"),
    axis.ticks = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.7)
  )

@@

```{r richness, width = 7, height = 4}
# Richness
a <- ggplot(ses_div_ferns_spatial, aes(fill = richness)) +
  geom_sf(color = "transparent") +
  scale_fill_scico(palette = "lajolla") + 
  labs(fill = "Richness") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme

# Sampling rendundancy
b <- ggplot(ses_div_ferns_spatial, aes(fill = redundancy)) +
  geom_sf(color = "transparent") +
  scale_fill_scico(palette = "lajolla") + 
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  labs(fill = "Redundancy") +
  map_theme +
  theme(
    axis.text.y = element_blank()
  )

ggsave(result_file(figure("richness"), "pdf"), width = 7, height = 4, units = "in")
```

**`r figure("richness")`**. `r figure_cap("diversity")` **A**, richness. **B**, sampling redundancy.

```{r diversity, fig.width = 7, fig.height = 9}
# PD
a <- ggplot(ses_div_ferns_spatial, aes(fill = pd_obs)) +
  geom_sf(color = "transparent") +
  labs(fill = "PD") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  scale_fill_scico(palette = "lajolla") + 
  map_theme +
  theme(
    axis.text.x = element_blank()
  )

# SES of PD
b <- ggplot(ses_div_ferns_spatial, aes(fill = pd_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES PD") +
  scale_fill_scico(
    palette = "romaO",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, pd_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, pd_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank()
  )

# RPD
c <- ggplot(ses_div_ferns_spatial, aes(fill = rpd_obs)) +
  geom_sf(color = "transparent") +
  labs(fill = "RPD") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  scale_fill_scico(palette = "lajolla") + 
  map_theme +
  theme(
    axis.text.x = element_blank()
  )

# SES of RPD
d <- ggplot(ses_div_ferns_spatial, aes(fill = rpd_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES RPD") +
  scale_fill_scico(
    palette = "roma",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, rpd_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, rpd_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  # highlight only significant cells
  # gghighlight(pd_obs_p > 0.975 | pd_obs_p < 0.025) +
  map_theme +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank()
  )

# FD
e <- ggplot(ses_div_ferns_spatial, aes(fill = fd_obs)) +
  geom_sf(color = "transparent") +
  labs(fill = "FD") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  scale_fill_scico(palette = "lajolla") + 
  map_theme +
  theme(
    axis.text.x = element_blank()
  )

# SES of FD
f <- ggplot(ses_div_ferns_spatial, aes(fill = fd_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES FD") +
  scale_fill_scico(
    palette = "roma",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, fd_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, fd_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  # highlight only significant cells
  # gghighlight(mpd_morph_obs_p > 0.975 | mpd_morph_obs_p < 0.025) +
  map_theme +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank()
  )

# RFD
g <- ggplot(ses_div_ferns_spatial, aes(fill = rfd_obs)) +
  geom_sf(color = "transparent") +
  labs(fill = "RFD") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  scale_fill_scico(palette = "lajolla") + 
  map_theme

# SES of RFD
h <- ggplot(ses_div_ferns_spatial, aes(fill = rfd_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES RFD") +
  scale_fill_scico(
    palette = "roma",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, rfd_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, rfd_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  # highlight only significant cells
  # gghighlight(rfd_obs_p > 0.975 | rfd_obs_p < 0.025) +
  map_theme +
  theme(
    axis.text.y = element_blank()
  )

@@

**`r figure("diversity")`**. `r figure_cap("diversity")` **A**, Phylogenetic diversity (PD). **B**, Standard effect size (SES) of PD. **C**, Relative phylogenetic diversity (RPD). **D**, SES of RPD. **E**, Functional diversity (FD). **F**, SES of FD **G**, Relative functional diversity (RFD) **H**, SES of RFD.

@@

```{r endemism, fig.width = 7, fig.height = 8}
# PE
a <- ggplot(ses_div_ferns_spatial, aes(fill = pe_obs)) +
  geom_sf(color = "transparent") +
  scale_fill_scico(palette = "lajolla") + 
  labs(fill = "PE") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme +
  theme(
    axis.text.x = element_blank()
  )

# PE rank
b <- ggplot(ses_div_ferns_spatial, aes(fill = pe_obs_rank)) +
  geom_sf(color = "transparent") +
  labs(fill = "Rank PE") +
  scale_fill_scico(palette = "lajolla") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank()
  )

# RPE
c <- ggplot(ses_div_ferns_spatial, aes(fill = rpe_obs)) +
  geom_sf(color = "transparent") +
  scale_fill_scico(palette = "lajolla") +
  labs(fill = "RPE") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme +
  theme(
    axis.text.x = element_blank()
  )

# SES RPE
d <- ggplot(ses_div_ferns_spatial, aes(fill = rpe_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES RPE") +
  scale_fill_scico(
    palette = "roma",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, rpe_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, rpe_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme +
  theme(
    axis.text.y = element_blank()
  )

# CANAPE, full dataset
# set color scheme
canape_cols <- c(
  "neo" = "#E41A1C", # Color brewer set1 red
  "paleo" = "#377EB8", # Color brewer blue
  "mixed" = "#984EA3", # Color brewer purple
  "none" = "#FFFFCC" # Scico lajolla faintest color
)

e <- 
  ses_div_ferns_spatial %>%
  mutate(endem_type = replace_na(endem_type, "none")) %>%
  ggplot(aes(fill = endem_type)) +
  geom_sf(color = "transparent") +
  labs(fill = "Endemism\ntype") +
  scale_fill_manual(values = canape_cols, breaks = c("neo", "paleo", "mixed", "none"), labels = c("Neo", "Paleo", "Mixed", "Not endemic")) + 
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme_light

@@

```{r bioregions, fig.width = 7, fig.height = 3}
# Taxonomic bioregions
a <- ggplot(ses_div_ferns_spatial, aes(fill = taxonomic_cluster)) +
  geom_sf(color = "transparent") +
  scale_fill_carto_d(name = "Cluster", type = "qualitative", palette = "Bold") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme_light

# Phylogenetic bioregions
b <- ggplot(ses_div_ferns_spatial, aes(fill = phylo_cluster)) +
  geom_sf(color = "transparent") +
  labs(fill = "Cluster") +
  scale_fill_carto_d(name = "Cluster", type = "qualitative", palette = "Bold") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme_light

@@

```{r diversity-by-cluster, fig.width = 7, fig.height = 7}
data <-
ses_div_ferns_spatial %>%
  filter(taxonomic_cluster %in% c(1,2,3,4)) %>%
  as_tibble %>%
  select(pd_obs_z, rpd_obs_z, fd_obs_z, rfd_obs_z, pe_obs_rank, taxonomic_cluster)

cluster_cols <- carto_pal(8, "Bold")[1:4] %>%
  set_names(1:4)

a <- ggplot(data, aes(x = taxonomic_cluster, y = pd_obs_z)) +
  geom_jitter(aes(color = taxonomic_cluster)) +
  scale_color_manual(values = cluster_cols, breaks = 1:4) +
  geom_boxplot(color = "grey80", fill = "transparent", outlier.shape = NA, alpha = 0.25) +
  labs(
    y = "SES PD",
    x = "Cluster",
    color = "Cluster"
  ) +
  theme_bw() +
  theme(
    panel.grid.minor.x = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank()
  )

b <- ggplot(data, aes(x = taxonomic_cluster, y = rpd_obs_z)) +
  geom_jitter(aes(color = taxonomic_cluster)) +
  scale_color_manual(values = cluster_cols, breaks = 1:4) +
  geom_boxplot(color = "grey80", fill = "transparent", outlier.shape = NA, alpha = 0.25) +
  labs(
    y = "SES RPD",
    x = "Cluster",
    color = "Cluster"
  ) +
  theme_bw() +
  theme(
    panel.grid.minor.x = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank()
  )

c <- ggplot(data, aes(x = taxonomic_cluster, y = fd_obs_z)) +
  geom_jitter(aes(color = taxonomic_cluster)) +
  scale_color_manual(values = cluster_cols, breaks = 1:4) +
  geom_boxplot(color = "grey80", fill = "transparent", outlier.shape = NA, alpha = 0.25) +
  labs(
    y = "SES FD",
    x = "Cluster",
    color = "Cluster"
  ) +
  theme_bw() +
  theme(
    panel.grid.minor.x = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank()
  )

d <- ggplot(data, aes(x = taxonomic_cluster, y = rfd_obs_z)) +
  geom_jitter(aes(color = taxonomic_cluster)) +
  scale_color_manual(values = cluster_cols, breaks = 1:4) +
  geom_boxplot(color = "grey80", fill = "transparent", outlier.shape = NA, alpha = 0.25) +
  labs(
    y = "SES RFD",
    x = "Cluster",
    color = "Cluster"
  ) +
  theme_bw() +
  theme(
    panel.grid.minor.x = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    axis.title.x = element_blank()
  )

e <- ggplot(data, aes(x = taxonomic_cluster, y = pe_obs_rank)) +
  geom_jitter(aes(color = taxonomic_cluster)) +
  scale_color_manual(values = cluster_cols, breaks = 1:4) +
  geom_boxplot(color = "grey80", fill = "transparent", outlier.shape = NA, alpha = 0.25) +
  labs(
    y = "Rank PE",
    x = "Cluster",
    color = "Cluster"
  ) +
  theme_bw() +
  theme(
    panel.grid.minor.x = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.y = element_blank(),

  )

a + b + c + d + e +
  plot_layout(ncol = 2) +
plot_annotation(
  tag_levels = 'A'
) &
  theme(legend.position = "none")

ggsave(result_file(figure("div-by-tax-region"), "pdf"), width = 7, height = 7, units = "in")

**`r figure("div-by-tax-region")`**. `r figure_cap("div-by-tax-region")`. **A**, Standard effect size (SES) of phylogenetic diversity (PD). **B**, SES of relative PD (RPD). **C**, SES of functional diversity (FD). **D**, SES of relative FD (RFD). **E**, rank of observed phylogenetic endemism (PE) out of 999 random communities. Only top four clusters with the most sites shown.
